---
title: "IO optimization report"
author: "James Azam"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE,echo=FALSE}
library(tidyverse)
library(rstan)
```


```{r message=FALSE,echo=TRUE}
#Load one full output
full_output <- readRDS(file.path('./outputs/full/const_const_const_const.rds'))
```


# File sizes
## Full object
This is the full output of `estimate_secondary()`, which is a list containing three objects: predictions, fit, and data.

```{r}
full_obj_size <- object.size(full_output)

print(full_obj_size, units = 'Mb', standard = 'legacy')

```

## Prediction object
This object contains the raw data as well as summaries of the model predictions.

```{r}
pred_obj <- pluck(full_output, 'predictions')

pred_obj_size <- object.size(pred_obj)

head(pred_obj, n = 5)

print(pred_obj_size, units = 'Kb', standard = 'legacy')
```

# Fit object
This is where all the heavy stuff are stored, and probably forms over 99% of the total size, most of which we don't need at the moment.

```{r}
fit_obj <- pluck(full_output, 'fit')

fit_obj_size <- object.size(fit_obj)

print(fit_obj_size, units = 'Mb', standard = 'legacy')
```



## Fit summary object
Running `summary` on the fit object returns to summary objects, one of which is the merged summaries of the individual chains and the other one "c_summary" contains the raw statisyics from the individual chains. Currently, we only need the merged summary object.

```{r}
fit_summary_obj <- pluck(summary(full_output$fit), 'summary') %>% 
  as_tibble(rownames = 'simplex')

fit_summary_obj_size <- object.size(fit_summary_obj)

print(fit_summary_obj_size, units = 'Kb', standard = 'legacy')
```

## Data object

This object is a list containing the raw data and other rstan model inputs/outputs. 

```{r}
data_obj <- pluck(full_output, 'data')

data_obj_size <- object.size(data_obj)

print(data_obj_size, units = 'Kb', standard = 'legacy')
```
